Radial and rotational velocities of young brown dwarfs and very low-mass stars in the Upper Scorpius OB association and the $\rho$~Ophiuchi cloud core

### 2006-08-18 BD_radvel/mn060888mj_rev/kurosawa.tex
Th revision still in progress.
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@783 25464f21-6099-402c-b30a-640f1d40d38b

Before applying the cross-correlation technique to our main targets,
we have applied the technique to the radial velocity standard HD~140538
for which an high-accuracy RV measurement via the fixed-configuration,
cross-dispersed échelle spectrograph Elodie \citep{baranne:1996}
is available. This was done so to ensure not only the validity of
the cross-correlation technique, but also the validity of the wavelength
calibration. In this test, we found the heliocentric $\mathrm{RV_{HD\,140538}=}19.18\pm0.62\,\kmps$
which is in good agreement with the Elodie radial velocity measurement
of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep*{udry:1999}.

@@

We have computed $p$ for all the objects (Table~\ref{tab:chisq_prob}),
and have plotted the results  
as a histogram of $-\log{p}$, shown in Fig.~\ref{fig:chisq-test}
(excluding the non-member USco~121; see explanation later). 
The figure clearly shows two distinctive populations: one on the left
(with small $-\log{p}$ values) occupied by the RV constant objects,
and one on the right (with the large $-\log{p}$ values)
occupied by the RV variable candidates.  The
expected distribution of $p$ computed consistently with our
uncertainty measurements is also shown in the same figure. The RV
constant population on the left side reasonably matches the expected
curve. This reassures that our uncertainties in RV values are
reasonable, and an additional systematic error may not be necessary in
this analysis. 
The boundary ($p=10^{-3}$) between the RV variable and the RV
constants seems somewhat arbitrary, but here we simply adopt the
definition of \citet{maxted:2005}.  Based on this criteria, there are
four objects which show significant RV variations (out of 17 samples)
as one can see from the figure.   They are USco~112, USco~128,
USco~40, and USco~55, and considered as our preliminary binary/multiple 
candidates.  We will discuss the binary fraction and the expected binary
detection probability later in Section~\ref{sec:Binary-fraction}.

>>>>

Before applying the cross-correlation technique to our main targets,
we have applied the technique to the radial velocity standard
HD~140538 \textcolor{red}{(G2.5V)}
for which an high-accuracy RV measurement via the fixed-configuration,
cross-dispersed \'{e}celle spectrograph Elodie \citep{baranne:1996}
is available. This was done so to ensure not only the validity of
the cross-correlation technique, but also the validity of the wavelength
calibration. In this test, we found the heliocentric 
\textcolor{red}{
$\mathrm{RV_{HD\,140538}=}19.17\pm0.40\,\kmps$
}
which is in good agreement with the Elodie radial velocity measurement
of $19.00\pm0.05\,\mathrm{km\, s^{-1}}$ \citep*{udry:1999}.
\textcolor{red}{
  Note that the uncertainty in $\mathrm{RV_{HD\,140538}}$ was computed
  by combining the uncertainty ($0.4~\kmps$) in the heliocentric RV of
  the template star HD~74497 (G3V)) and the uncertainty in the
  relative RV of HD~140538 ($0.02~\kmps$), measured with respect to
  the template star.  Clearly, the former dominates in the uncertainty
  in the value of $\mathrm{RV_{HD\,140538}}$ shown above. The
  uncertainty in the heliocentric RV of the template is rather large
  since it was determined from a few photospheric lines.
}

@@

We have computed $p$ for all the objects (Table~\ref{tab:chisq_prob}),
and have plotted the results  
as a histogram of $-\log{p}$, shown in Fig.~\ref{fig:chisq-test}
(excluding the non-member USco~121; see explanation later). 
The figure clearly shows two distinctive populations: one on the left
(with small $-\log{p}$ values) occupied by the RV constant objects,
and one on the right (with the large $-\log{p}$ values)
occupied by the RV variable candidates.  The
expected distribution of $p$ computed consistently with our
uncertainty measurements is also shown in the same figure. The RV
constant population on the left side reasonably matches the expected
curve. 
\textcolor{red}{To quantify this point, we have computed the
chi-square probability to test the goodness of the fit of the expected
distribution to the histogram. We restrict the fit to the first 4 bins
from the left $\left(0 < -\log_{10}\left(p\right) < 2 \right)$ the
histogram since the objects in the second bin from the right
$\left(2.5 < -\log_{10}\left(p\right) < 3 \right)$ are `potentially'
RV-variable object, although we have flagged them as the RV-constant
objects. In this analysis, we find the probability of 0.5 which
indicates that the fit is reasonable. Further, if we re-normalized the
expected distribution, accounting for that fact we neglected the
objects in the second bin from the right, we find the chi-square
probability of the fit increases to 0.9.  This, in turn, indicates}
that our uncertainties in RV values are reasonable, and an additional
systematic error may not be necessary in this analysis.

The boundary ($p=10^{-3}$) between the RV variable and the RV
constants seems somewhat arbitrary, but here we simply adopt the
definition of \citet{maxted:2005}.  Based on this criteria, there are
four objects which show significant RV variations (out of 17 samples)
as one can see from the figure.   They are USco~112, USco~128,
USco~40, and USco~55, and considered as our preliminary binary/multiple 
candidates.  We will discuss the binary fraction and the expected binary
detection probability later in Section~\ref{sec:Binary-fraction}.
